ms2

### 2017-08-18 ms2/ms2_display.Rmd
ms2 more models

@@

- a Spearman correlation of mean claims per beneficiary against mean percent nonsusceptible
- a linear model predicting mean resistance from mean consumption
- a linear model predicting mean resistance from fraction nonzero and nonzero Gini

@@

The plot shows the Spearman correlation coefficient $\rho$ between resistance $R$ and fraction $f_>$ of beneficiaries who are consumers. Two stars after the bug/drug combination implies that the adjusted $p < 0.05$, and one star means the unadjusted $p < 0.05$. Intervals show 95% confidence intervals.

@@

results %>%
  filter(model=='spearman', unit_type=='hrr') %>%
  interval_plot() +
  ylab("Spearman's rho") +
  ggtitle("Spearman, HRR")
```

```{r state_spearman}
results %>%
  filter(model=='spearman', unit_type=='state') %>%
  interval_plot() +
  ylab("Spearman's rho") +
  ggtitle("Spearman, state")
```

@@

@@

```{r hrr_linear}
results %>%
  filter(model=='univariate_fnz', unit_type=='hrr', term=='fnz') %>%
  interval_plot() +
  geom_hline(yintercept=1, col='gray') +
  ylab(expression(beta[f])) +
  ggtitle("Linear univariate, HRR")
```

```{r state_linear}
results %>%
  filter(model=='univariate_fnz', unit_type=='state', term=='fnz') %>%
  interval_plot() +
  ylab(expression(beta[f])) +
  ggtitle("Linear univariate, state")
```

@@

```{r fnz_mup_tetra_bactrim}
ineq %>%
  #filter(unit_type=='hrr', drug_group %in% c('tetracycline', 'tmp_smx')) %>%
  filter(unit_type=='hrr') %>%
  filter(mup < 2.2) %>% # get rid of one outlier
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_out, by='hrr') %>%
  ggplot(aes(x=fnz, y=mup, color=region)) +
  facet_wrap(~drug_group, scales='free') +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='gray') +
  geom_smooth(method='lm', se=F) +
  geom_point(shape=1) +
  xlab(expression(f['>'])) +
  ylab(expression(mu['>'])) +
  ggtitle('Mean nonzero consumption vs. fraction consuming, states') +
  theme_minimal()
```

@@

```{r fnz_mean_region}
ineq %>%
  filter(unit_type=='state', drug_group == 'overall') %>%
  rename(state=unit) %>%
  filter(state != 'DC') %>%
  left_join(regions, by='state') %>%
  ggplot(aes(x=fnz, y=mean, color=region)) +
  geom_smooth(aes(color=NULL), method='lm', se=F, color='gray') +
  geom_point() +
  xlab('Fraction nonzero') + ylab('claims per beneficiary') +
  ggtitle('Fraction consuming and mean consumption, states') +
  theme_minimal()
```

@@

>>>>

I summarized the resistance data for each geographical unit with a weighted mean, where the weight was the square root of the number of isolates. (In the rare cases where the number of isolates was not reported, I put in the median number of isolates for that organism.)

@@

- a Spearman correlation of mean claims per beneficiary $\mu$ against mean percent nonsusceptible $R$
- a linear model predicting mean resistance from the fraction $f_>$ of people who are consumers
- a linear model predicting mean resistance from $f_>$ and mean consumption among consumers $\mu_> = \mu/f_>$.

When running regressions, I weight the data points by the number of antibiograms present in that unit. (The weights in a linear regression should be proportional to $1/\sigma^2$, and we generally expect that the standard error of estimators scales like $1/\sqrt{n}$.)

@@

The plot shows the Spearman correlation coefficient $\rho$ between resistance $R$ and mean consumption $\mu$. Two stars after the bug/drug combination implies that the adjusted $p < 0.05$, and one star means the unadjusted $p < 0.05$. Intervals show 95% confidence intervals.

@@

results %>%
  filter(model=='spearman', unit_type=='hrr') %>%
  interval_plot() +
  ylab("Spearman's rho") +
  ggtitle("Spearman, res. vs. mean consumption, HRR")
```

```{r state_spearman}
results %>%
  filter(model=='spearman', unit_type=='state') %>%
  interval_plot() +
  ylab("Spearman's rho") +
  ggtitle("Spearman, res. vs. mean consumption, state")
```

@@

We're interested in how it is that mean consumption drives resistance. Is it at the intensive or extensive margin? We separate that by writing $\mu = f_> \mu_>$.

@@

```{r hrr_linear}
results %>%
  filter(model=='univariate_fnz', unit_type=='hrr', term=='fnz') %>%
  interval_plot() +
  geom_hline(yintercept=1, col='gray') +
  ylab(expression(beta[f['>']])) +
  ggtitle("Linear univariate, HRR")
```

```{r state_linear}
results %>%
  filter(model=='univariate_fnz', unit_type=='state', term=='fnz') %>%
  interval_plot() +
  ylab(expression(beta[f['>']])) +
  ggtitle("Linear univariate, state")
```

Why should the linear models do so much better than the Spearman? I think it's because, in the linear model, I can weight the geographical units that have more antibiograms. The Spearman model treats them all equally.

@@

```{r fnz_mup_by_drug}
ineq %>%
  filter(unit_type=='hrr') %>%
  filter(mup < 2.2) %>% # get rid of one outlier
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_out, by='hrr') %>%
  ggplot(aes(x=fnz, y=mup, color=region)) +
  facet_wrap(~drug_group, scales='free') +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='gray') +
  geom_smooth(method='lm', se=F) +
  geom_point(shape=1) +
  xlab(expression(f['>'])) +
  ylab(expression(mu['>'])) +
  ggtitle('Mean nonzero consumption vs. fraction consuming, states') +
  theme_minimal()
```

@@

```{r fnz_mean_region}
ineq %>%
  filter(unit_type=='state', drug_group == 'overall') %>%
  rename(state=unit) %>%
  filter(state != 'DC') %>%
  left_join(regions, by='state') %>%
  ggplot(aes(x=fnz, y=mean, color=region)) +
  geom_smooth(aes(color=NULL), method='lm', se=F, color='gray') +
  geom_point() +
  xlab('Fraction nonzero') + ylab('claims per beneficiary') +
  ggtitle('All antibiotics, f> and mean consumption, states') +
  theme_minimal()
```

@@

Only the West has a significantly non-zero slope.

### E. coli & Bactrim, Part II

Weirdly, within each region, Bactrim resistance goes does as $\mu_>$ increases.

```{r}
hrr_ir = ineq %>%
  filter(unit_type=='hrr') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_out, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group'))

hrr_ir %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(mean_percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=mup, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('mean Bactrim cons. among Bactrim-eaters') +
  ylab('Bactrim-resistance E. coli') +
  ggtitle('E. coli & Bactrim, mu>, HRRs')
```

Here, the South and West have significantly non-zero slopes.

At least this explains, in a sense, why this relationship looks negative: the South is perched up high, so overall the black line goes down.
